Forecasting the 2024 US Presidential Election: A Poll-Based Approach

### 2024-10-30 paper/paper.qmd
Update 14 preliminary models

## Model set-up
```{r}
#| echo: false
#| message: false
#| warning: false
candidate_names <- c("Kamala Harris", "Donald Trump")

# Define a function to fit the model and return the summary for each candidate
fit_model <- function(candidate) {
  candidate_data <- data %>%
    filter(candidate_name == candidate)

  model <- lm(pct ~ pollscore + transparency_score + sample_size + state + days_towards_election, data = candidate_data)

  summary(model)
}

# Apply the function to each distinct candidate name and store the summaries in a list
model_summaries <- candidate_names %>%
  set_names() %>%
  map(fit_model)

# Print model summaries for each candidate
model_summaries
```

>>>>

## Model set-up
```{r}
#| echo: false
#| message: false
#| warning: false
data_nevada <- data %>% filter(state == "Nevada") 
data_arizona <- data %>% filter(state == "Arizona") 
data_wisconsin <- data %>% filter(state == "Wisconsin") 
data_michigan <- data %>% filter(state == "Michigan") 
data_penn <- data %>% filter(state == "Pennsylvania") 
data_north_carolina <- data %>% filter(state == "North Carolina") 
data_georgia <- data %>% filter(state == "Georgia")

candidate_names <- c("Kamala Harris", "Donald Trump")

fit_model <- function(data, candidate) {
  candidate_data <- data %>% filter(candidate_name == candidate)

  if (nrow(candidate_data) > 0) {  # Check if there are rows for the candidate
    model <- lm(pct ~ days_towards_election, data = candidate_data)
    tidy_model <- tidy(model)  # Get a tidy summary of the model
    tidy_model$state <- unique(candidate_data$state)  # Add state to the output
    tidy_model$candidate <- candidate  # Add candidate to the output
    return(tidy_model)
  } else {
    return(NULL)  # Return NULL if no data for the candidate
  }
}

state_data_list <- list(
  Nevada = data_nevada,
  Arizona = data_arizona,
  Wisconsin = data_wisconsin,
  Michigan = data_michigan,
  Pennsylvania = data_penn,
  North_Carolina = data_north_carolina,
  Georgia = data_georgia
)

# Initialize an empty list to store results
results <- list()

# Loop through each candidate
for (candidate in candidate_names) {
  state_results <- list()  # Initialize an empty list for state results

  # Loop through each state dataset
  for (state_name in names(state_data_list)) {
    state_data <- state_data_list[[state_name]]  # Get the state data
    model_result <- fit_model(state_data, candidate)  # Fit the model
    state_results[[state_name]] <- model_result  # Store the result
  }

  # Combine results for the current candidate into a single data frame
  results[[candidate]] <- bind_rows(state_results)
}

# Combine results for all candidates into a single data frame
final_results <- bind_rows(results, .id = "candidate")

# View the final results
print(final_results)

```{r}
intercept_results <- final_results %>%
  filter(term == "(Intercept)")

# Spread the results into wide format
intercept_wide <- intercept_results %>%
  select(state, candidate, estimate) %>%
  pivot_wider(names_from = candidate, values_from = estimate, values_fill = NA)

# Calculate the difference in estimates between candidates
intercept_wide <- intercept_wide %>%
  mutate(difference = `Kamala Harris` - `Donald Trump`)

# View the results with differences
print(intercept_wide)
```

```{r}
